workshop

### 2023-03-01 scripts/workshop/workshop.Rmd
knit it
add code folding

---
title: "workshop"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

@@

effect_summ_2 <- comm_effect_2 %>% group_by(WetAltID) %>% summarize(size_over = sum(size_sds>0),
                                                                size_sum = sum(size_sds),
                                                                cc_over = sum(cc_sds>0),
                                                                cc_sum = sum(cc_sds),
                                                                temp_over = sum(temp_sds>0),
                                                                temp_sum = sum(temp_sds))
```

@@

>>>>

---
title: "workshop"
author: "Daniel Suh"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

@@

effect_summ_2 <- comm_effect_2 %>% group_by(WetAltID) %>% summarize(n = n(),
                                                                size_over = sum(size_sds>0),
                                                                size_sum = sum(size_sds),
                                                                cc_over = sum(cc_sds>0),
                                                                cc_sum = sum(cc_sds),
                                                                temp_over = sum(temp_sds>0),
                                                                temp_sum = sum(temp_sds))
effect_summ_2
```

@@

```{r}

```
